Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
Made final edits

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Websites are malleable: users can run code in the browser to customize
  them. However, this malleability is typically only accessible to
  programmers with knowledge of HTML and Javascript. Previously, we
  developed a tool called Wildcard which empowers end-users to customize
  websites through a data table interface without doing traditional
  programming. However, there is a limit on end-user flexibility with
  Wildcard, because programmers need to create site-specific adapters
  mapping website data to a table view. This means that end-users can
  only customize a website if a programmer has written an adapter for
  it, and cannot extend or repair existing adapters.

  In this paper, we extend Wildcard with a new system for \emph{end-user
  web scraping for customization}. It enables end-users to create,
  extend and repair adapters, by performing concrete demonstrations of
  how the webpage UI maps to a data table. We describe three design
  principles that guided our system's development and are applicable to
  other end-user web scraping and customization systems: (a) users
  should be able to scrape data and use it in a single, unified
  environment, (b) users should be able to extend and repair the
  programs that scrape data via demonstration and (c) users should
  receive live feedback during their demonstrations.

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites and we provide
  example usage scenarios that showcase each of our design principles.
\end{abstract}

@@

Many websites on the internet do not meet the exact needs of all of
their users. End-user web customization systems like Chickenfoot
\citep{bolin2005}, Thresher \citep{hogue2005}, Sifter \citep{huynh2006}
and Vegemite \citep{lin2009} help users tweak and adapt websites to fit
their unique requirements, ranging from reorganizing or annotating
content on the website to automating common tasks. In our prior work, we
presented Wildcard \citep{litt2020a}, a customization system which
enables end-users to customize websites through direct manipulation. It
does this by augmenting websites with a table view that shows their
underlying structured data. The table is bidirectionally synchronized
with the original website, so end-users can easily customize the website
by interacting with the table, including sorting and filtering data,
adding annotations, and running computations in a spreadsheet formula
language.

@@

Finally, we share our broader vision for web scraping for customization,
and some opportunities for future work, including a proposal for how
Wildcard's spreadsheet-like formula language might augment
demonstrations to provide end-users with more expressiveness in the web
scraping process (Section~\ref{sec:conclusion}).

@@

\begin{itemize}
\tightlist
\item
  The selected row of data is annotated in the page with a border, to
  indicate that she will be demonstrating values from within that row
  (Part 3).
\item
  The selected column of data is highlighted in the page with a green
  background, to show how the system has generalized her demonstration
  across all the rows in the data (Part 4).
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table (Part 5).
\end{itemize}

@@

Jen next visits Google Scholar to look up references for her thesis
project. Unfortunately, the customization she had applied to sort
publications by their title (which is not natively supported by Google
Scholar) is no longer working. In fact, the column in the Wildcard table
that contained all the publication titles is empty, because the
website's internals changed and broke the adapter's scraping logic. Jen
can repair this on her own, again taking advantage of \textbf{editing by
demonstration}.

The workflow is shown in Figure~\ref{fig:repairing}. Jen initiates the
editing process (Part 2), and initially hovers over the desired value to
demonstrate the column she wants to scrape. However, the \textbf{live
programming} interface indicates to her that the values would be
populated into column D; instead, she wants the values to be inserted
into column A where they previously appeared. So, Jen clicks on the
symbol for column A (Part 3) to indicate that she wants to scrape the
values into that column and demonstrates the first publication title
(Part 4). The missing values are now back in the table (Part 5). She
then proceeds to save her changes (Part 6) and re-apply her
customization to the website by sorting the publications by their title
without the intervention of a programmer.

@@

At a high level, the generalization algorithm's challenge is to traverse
far enough up in the DOM tree from the demonstrated element to find the
element which corresponds to the row. We solve this using a heuristic;
the basic intuition is to find a large set of elements with similar
parallel structure. Consider the following sample HTML layout, which
displays a truncated table of superheroes, with each row containing some
nested structure:

@@

The user performs a demonstration by clicking on element (a) in
Figure~\ref{fig:algorithm} containing ``Tony Stark.'' Our algorithm
traverses upwards from the demonstrated element, considering each
successive parent element ((b1), (c1) and (d) in
Figure~\ref{fig:algorithm}) as a potential candidate for the row
element. For each parent element \texttt{el}, the process is as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  compute a column selector \texttt{selector} that, when executed on
  \texttt{el}, only returns the demonstrated element
\item
  for each sibling \texttt{el\textquotesingle{}} of \texttt{el}, execute
  \texttt{selector} on \texttt{el\textquotesingle{}} and record whether
  the selector returns an element. If it does, this suggests that
  \texttt{el\textquotesingle{}} has some parallel structure to
  \texttt{el}.
\item
  compute \(n_{siblings}\), the number of sibling elements of
  \texttt{el} which have parallel structure.
\end{enumerate}

Notice how the \emph{row-sibling} constraint simplifies the problem. Row
candidates without siblings with parallel structure ((b1) in
Figure~\ref{fig:algorithm}) have \(n_{siblings}\) = 0, thus
disqualifying them.

The algorithm stops traversing upwards once it reaches the BODY element.
It chooses the element with the largest positive value of
\(n_{siblings}\) as the row element, preferring nodes lower in the tree
as a tiebreaker. It then generates a \emph{row selector} which returns
the row element and all its direct siblings. The column selector is the
selector that traverses from the row element to the demonstrated data
value. These row and column selectors are then used to generate a
scraping adapter which returns the DOM elements corresponding to a data
row in the table and sets up the bidirectional synchronization.

@@

Live programming is implemented by continually running the
generalization algorithm on the DOM element under the user's cursor,
reverting if the user hovers away and committing when the user clicks.
The generated row and column selectors are used to highlight all the
matching elements on the website and create an adapter. Highlighting all
the matching column elements on the website provides visual feedback
about the system's generalization to the user. Creating an adapter
enables the system to populate the table view and set up the
bidirectional synchronization. Because the table is populated and the
bidirectional synchronization is set up, users can customize as they
scrape.

@@

Extending and repairing adapters in this manner is feasible because
column selectors are independent of each other: changing one column's
selector does not affect another column's selector. This is not the case
for system's in which the output of demonstrations are dependent on each
other. For example, in a web automation sequence that involves clicking
on a button to open a menu and then entering text into the menu's text
input, the step that enters the text is not independent because it
depends on the step that clicks the button to open the menu.

@@

@@

\emph{Generalization Limitation 1} shows a case where the data is
displayed in a grouped structure. Without the constraint that row
elements have to be direct siblings, the row generalization algorithm
could determine the row selector to be \emph{.avenger} (elements with
blue border) because it matches the largest number of parallel
structures (has the largest \(n_{siblings}\)). While this may be the
correct result for the task of extraction, it is not necessarily
suitable for the task of customization. When the user sorts and filters,
this could result in rows moving between the two tables, disrupting the
nested layout and producing a confusing result. Because of this, our
system currently does not support such layouts. In the future, we may
explore the possibility of extracting multiple tables from a website and
joining them together.

\emph{Generalization Limitation 2}, also in
Figure~\ref{fig:limitations}, shows a case where the website contains
one table of data in which rows are made up of alternating H1 and SPAN
tags (elements with blue border). This poses a challenge because each
row does not correspond directly to a single DOM element; instead, each
row consists of multiple consecutive DOM elements without any grouped
structure. Moving the rows when customizing the webpage would require
treating multiple consecutive elements as a single row. This is
supported in the underlying Wildcard system, but not yet by our tool.

Our system also does not support scraping data loaded after the initial
websites render as the user scrolls. Site adapters hand-coded in
Javascript can specify event listeners on the DOM to re-execute the
scraping code when new data is loaded as a user scrolls. In future work,
we plan to provide a mechanism for end-users to specify when a
demonstrated adapter should re-execute its scraping code in response to
user scrolling. We also do not support scraping data across multiple
pages of related data, but this context poses more fundamental
challenges to the idea of web customization, since users would somehow
need to perform customizations across multiple pages in coordination.

@@

In this work, we have combined scraping and customization into a single,
unified environment with a unified workflow. The goal is to minimize the
environment switch between \emph{extracting} the data and \emph{using}
the data. A user might start out by scraping some data on a website, and
then switch to customizing the website using the results. Then, they
might realize they need more data to perform their desired task, at
which point they can easily extend the adapter by demonstrating new
columns. All of these tasks take place right in the browser, where the
user was initially already using the website. Instead of bringing the
data to another tool, we have brought a tool to the data. This principle
relates to the idea of ``in-place toolchains'' \citep{zotero-1362} for
end-user programming systems: that users should be able to program using
familiar tools in the context where they already use their software.

@@

Vegemite \citep{lin2009} is a tool for end-user programming of mashups.
It has two interfaces: one for scraping values from a website and
another for creating scripts that operate on the scraped values. The web
scraping interface does not provide live feedback about the
generalization on hover but after a user clicks a value, the interface
shows the result of the system's generalization by highlighting the all
matched values. Furthermore, even though the interface also has a table,
the table is only populated with the scraped values after all the
demonstrations have been provided. The scripting interface utilizes
CoScripter \citep{leshed2008} which is used to record operations on the
scraped values for automation. For example, the scripting interface can
be used to demonstrate the task of copying an address in the table,
pasting it into a walk score calculator and pasting the result back into
the table. The script would then be generalized to all the rows and
re-run to fill in the remaining walk scores. CoScripter provides the
generated automation program as text-based commands, such as ``paste
address into `Walk Score' input,'' which can be edited after the program
is created via ``sloppy programming'' \citep{lin2009} techniques.
However, this editing does not extend to the web scraping interface used
for demonstrations and presents a change in the model used for creation.

Sifter \citep{huynh2006} is a tool that augments websites with advanced
sorting and filtering functionality. Similarly to Wildcard, it uses web
scraping techniques to extract data from websites in order to enable
customizations. However, Wildcard supports a broader range of
customizations beyond sorting and filtering, including adding
annotations to websites and running computations with a spreadsheet
formula language. Our scraping tool intentionally provides less
automation than Sifter. Sifter attempts to automatically detect items
and fields on the page with a variety of clever heuristics, including
automatically detecting link tags and considering the size of elements
on the page. It then gives the user the option of correcting the result
if the heuristics do not work properly. In contrast, our heuristics are
simpler and make fewer assumptions about the structure of websites.
Rather, we give more control to the user from the beginning of the
process, and incorporate live feedback to help the user provide useful
demonstrations. We hypothesize that focusing on a tight feedback loop
rather than automation may support a scraping process that is just as
fast as an automated one, but gives the user finer control and extends
to a greater variety of websites where more complex heuristics do not
apply. However, further user testing is required to actually validate
this hypothesis.

@@

Our end goal is to empower end-users to customize websites in an
intuitive and flexible way, and thus make the web more malleable for all
of its users.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Websites are malleable: users can run code in the browser to customize
  them. However, this malleability is typically only accessible to
  programmers with knowledge of HTML and Javascript. Previously, we
  developed a tool called Wildcard which empowers end-users to customize
  websites through a spreadsheet-like table interface without doing
  traditional programming. However, there is a limit to end-user agency
  with Wildcard, because programmers need to first create site-specific
  adapters mapping website data to the table interface. This means that
  end-users can only customize a website if a programmer has written an
  adapter for it, and cannot extend or repair existing adapters.

  In this paper, we extend Wildcard with a new system for \emph{end-user
  web scraping for customization}. It enables end-users to create,
  extend and repair adapters, by performing concrete demonstrations of
  how the website user interface maps to a data table. We describe three
  design principles that guided our system's development and are
  applicable to other end-user web scraping and customization systems:
  (a) users should be able to scrape data and use it in a single,
  unified environment, (b) users should be able to extend and repair the
  programs that scrape data via demonstration and (c) users should
  receive live feedback during their demonstrations.

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites and we provide
  example usage scenarios that showcase each of our design principles.
  Our ultimate goal is to empower end-users to customize websites in an
  intuitive and flexible way, and thus make websites more malleable for
  all of its users.
\end{abstract}

@@

Many websites on the internet do not meet the exact needs of all of
their users. End-user web customization systems like Thresher
\citep{hogue2005}, Sifter \citep{huynh2006} and Vegemite \citep{lin2009}
help users tweak and adapt websites to fit their unique requirements,
ranging from reorganizing or annotating content on the website to
automating common tasks. In our prior work, we presented Wildcard
\citep{litt2020a}, a customization system which enables end-users to
customize websites through direct manipulation. It does this by
augmenting websites with a table view that shows their underlying
structured data. The table is bidirectionally synchronized with the
original website, so end-users can easily customize the website by
interacting with the table, including sorting and filtering data, adding
annotations, and running computations in a spreadsheet formula language.

@@

Finally, we share our broader vision for \emph{end-user web scraping for
customization}, and some opportunities for future work, including a
proposal for how Wildcard's spreadsheet-like formula language might
augment demonstrations to provide end-users with more expressiveness in
the web scraping process (Section~\ref{sec:conclusion}).

@@

\begin{itemize}
\tightlist
\item
  The row of data is annotated in the page with a border, to indicate
  that she will be demonstrating values from within that row (Part 3).
\item
  The column of data is highlighted in the page with a green background,
  to show how the system has generalized her demonstration across all
  the rows in the data (Part 4).
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table (Part 5).
\end{itemize}

@@

Jen next visits Google Scholar to look up references for a project.
Unfortunately, the customization she had applied to sort publications by
their title (which is not natively supported by Google Scholar) is no
longer working. In fact, the column in the Wildcard table that contained
all the publication titles is empty, because the website's internals
changed and broke the adapter's scraping logic. Jen can repair this on
her own, again taking advantage of \textbf{editing by demonstration}.

The workflow is shown in Figure~\ref{fig:repairing}. Jen initiates the
editing process (Part 2), and initially hovers over the desired value to
demonstrate the column she wants to scrape. However, the \textbf{live
programming} interface indicates to her that the values would be
populated into column D; instead, she wants the values to be inserted
into column A where they previously appeared. So, Jen clicks on the
symbol for column A (Part 3) to indicate that she wants to scrape the
values into that column and demonstrates the first publication title
(Part 4). The missing values are now back in the table (Part 5). She
then proceeds to save her changes (Part 6) and re-apply her
customization to the website by sorting the publications by their title.

@@

At a high level, the generalization algorithm's challenge is to traverse
far enough up in the DOM tree from the demonstrated element to find the
element which corresponds to the row. We solve this using a heuristic;
the basic intuition is to find a large set of elements with similar
parallel structure. Consider the sample HTML layout in
Figure~\ref{fig:algorithm}, which displays a truncated table of
superheroes, with each row containing some nested structure:

@@

The user performs a demonstration by clicking on element \(a\) in
Figure~\ref{fig:algorithm} containing ``Tony Stark.'' Our algorithm
traverses upwards from the demonstrated element, considering each
successive parent element (\(b1\), \(c1\) and \(d\) in
Figure~\ref{fig:algorithm}) as a potential candidate for the row
element. For each parent element \texttt{el}, the process is as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  compute a column selector \texttt{selector} that, when executed on
  \texttt{el}, only returns the demonstrated element
\item
  for each sibling \texttt{el\textquotesingle{}} of \texttt{el}, execute
  \texttt{selector} on \texttt{el\textquotesingle{}} and record whether
  the selector returns an element. If it does, this suggests that
  \texttt{el\textquotesingle{}} has some parallel structure to
  \texttt{el}.
\item
  compute \(el_{siblings}\), the number of sibling elements of
  \texttt{el} which have parallel structure.
\end{enumerate}

Notice how the \emph{row-sibling} constraint simplifies the problem. Row
candidates without siblings with parallel structure (\(b1\) in
Figure~\ref{fig:algorithm}) have \(el_{siblings}\) = 0, thus
disqualifying them.

The algorithm stops traversing upwards once it reaches the \texttt{BODY}
element. It chooses the element with the largest positive value of
\(el_{siblings}\) as the row element, preferring nodes lower in the tree
as a tiebreaker. It then generates a \emph{row selector} which returns
the row element and all its direct siblings. The final value of
\texttt{selector} is the column selector since traverses from the row
element to the demonstrated data value. These row and column selectors
are then used to generate a scraping adapter which returns the DOM
elements corresponding to a data row in the table and sets up the
bidirectional synchronization.

@@

Live programming is implemented by continually running the
generalization algorithm on the DOM element under the user's cursor,
reverting if the user hovers away and committing when the user clicks.
The generated row and column selectors are used to highlight all the
matching elements on the website and create an adapter. Highlighting all
the matching column elements on the website provides visual feedback
about the system's generalization to the user. Creating an adapter
enables the system to populate the table view and set up the
bidirectional synchronization. Because the table is populated and the
bidirectional synchronization is set up, users can customize as they
scrape. Live programming is possible in our system because the
generalization algorithm and adapters execute very quickly. We are yet
to benchmark the performance and compare it to other
programming-by-demonstration systems like FlashExtract \citep{le2014}
that that provide live feedback.

@@

Extending and repairing adapters in this manner is feasible because
column selectors are independent of each other: changing one column's
selector does not affect another column's selector. This is not the case
for systems in which the output of demonstrations are dependent on each
other. For example, in a web automation sequence that involves clicking
on a button to open a menu and then entering text into the menu's text
input, the step that enters the text is not independent because it
depends on the step that clicks the button to open the menu.

@@

\hypertarget{generalization-algorithm}{%
\subsection{Generalization Algorithm}\label{generalization-algorithm}}

@@

\emph{Generalization Limitation 1} shows a case where the data is
displayed in a grouped structure. Without the constraint that row
elements have to be direct siblings, the row generalization algorithm
could determine the row selector to be \emph{.avenger} (elements with
blue border) because it matches the largest number of parallel
structures (has the largest \(el_{siblings}\)). While this may be the
correct result for the task of extraction, it is not necessarily
suitable for the task of customization. When the user sorts and filters,
this could result in rows moving between the two tables, disrupting the
nested layout and producing a confusing result. Because of this, our
system currently does not support such layouts. In the future, we may
explore the possibility of extracting multiple tables from a website and
joining them together.

\emph{Generalization Limitation 2}, also in
Figure~\ref{fig:limitations}, shows a case where the website contains
one table of data in which rows are made up of alternating \texttt{H1}
and \texttt{SPAN} tags (elements within blue border). This poses a
challenge because each row does not correspond directly to a single DOM
element; instead, each row consists of multiple consecutive DOM elements
without any grouped structure. Moving the rows when customizing the
website would require treating multiple consecutive elements as a single
row. This is supported in the underlying Wildcard system, but not yet by
our demonstration-based approach.

\hypertarget{data-loaded-after-initial-render}{%
\subsection{Data Loaded After Initial
Render}\label{data-loaded-after-initial-render}}

Our currently system does not support scraping data loaded after the
initial websites render as the user scrolls. Site adapters hand-coded in
Javascript can specify event listeners on the DOM to re-execute the
scraping code when new data is loaded as a user scrolls. In future work,
we plan to provide a mechanism for end-users to specify when a
demonstrated adapter should re-execute its scraping code in response to
user scrolling. We also do not support scraping data across multiple
pages of related data, but this context poses more fundamental
challenges to the idea of web customization, since users would somehow
need to perform customizations across multiple pages in coordination.

@@

In this work, we have combined scraping and customization into a single,
unified environment with a unified workflow. The goal is to minimize the
environment switch between \emph{extracting} the data and \emph{using}
the data. A user might start out by scraping some data on a website, and
then switch to customizing the website using the results. Then, they
might realize they need more data to perform their desired task, at
which point they can easily extend the adapter by demonstrating new
columns. All of these tasks take place right in the browser, where the
user was initially already using the website. Instead of bringing the
data to another tool, we have brought a tool to the data. This principle
relates to the idea of ``in-place toolchains'' \citep{zotero-1362} for
end-user programming systems: users should be able to program using
familiar tools in the context where they already use their software.

@@

Vegemite \citep{lin2009} is a tool for end-user programming of mashups.
It has two interfaces: one for scraping values from a website and
another for creating scripts that operate on the scraped values. The web
scraping interface does not provide live feedback about the
generalization on hover but after a user clicks a value, the interface
shows the result of the system's generalization by highlighting the all
matched values. Furthermore, even though the interface also has a table,
the table is only populated with the scraped values after all the
demonstrations have been provided. The scripting interface utilizes
CoScripter \citep{leshed2008} which is used to record operations on the
scraped values for automation. For example, the scripting interface can
be used to demonstrate the task of copying an address in the data table,
pasting it into a walk score calculator and pasting the result back into
the table. The script would then be generalized to all the rows and
re-run to fill in the remaining walk scores. CoScripter provides the
generated automation program as text-based commands, such as ``paste
address into `Walk Score' input,'' which can be edited after the program
is created via ``sloppy programming'' \citep{lin2009} techniques.
However, this editing does not extend to the web scraping interface used
for demonstrations and presents a change in the model used for creation.

Sifter \citep{huynh2006} is a tool that augments websites with advanced
sorting and filtering functionality. Similarly to Wildcard, it uses web
scraping techniques to extract data from websites in order to enable
customizations. However, Wildcard supports a broader range of
customizations beyond sorting and filtering, including adding
annotations to websites and running computations with a spreadsheet
formula language. Our scraping system intentionally provides less
automation than Sifter. Sifter attempts to automatically detect items
and fields on the page with a variety of clever heuristics, including
automatically detecting link tags and considering the size of elements
on the page. It then gives the user the option of correcting the result
if the heuristics do not work properly. In contrast, our heuristics are
simpler and make fewer assumptions about the structure of websites.
Rather, we give more control to the user from the beginning of the
process, and incorporate live feedback to help the user provide useful
demonstrations. We hypothesize that focusing on a tight feedback loop
rather than automation may support a scraping process that is just as
fast as an automated one, but gives the user finer control and extends
to a greater variety of websites where more complex heuristics do not
apply. However, further user testing is required to actually validate
this hypothesis.

@@

Our ultimate goal is to empower end-users to customize websites in an
intuitive and flexible way, and thus make the web more malleable for all
of its users.
